Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-01-19 README.Rmd
updated readme and trying to get binder going

> Robinson, Erick, R. Kyle Bocinsky, Jacob Freeman, Darcy Bird, Robert L. Kelly, (2020). _`r Title`_. Under review.

@@

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, Robinson2020, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("bocinsky/robinson2020")
```

@@

>>>>

> Robinson, Erick [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-0789-3724), R. Kyle Bocinsky [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-1862-3428), Jacob Freeman, Darcy Bird [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0003-3466-6284), Robert L. Kelly, (2020). _`r Title`_. Under review.

@@

## Contents

The **analysis** directory contains:

- [:file_folder: paper](/analysis/paper): R Markdown source document for the manuscript. Includes code to reproduce the figures and tables generated by the analysis. It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)
- [:file_folder: data](/analysis/data): Data used in the analysis.  
- [:file_folder: figures](/analysis/figures): Plots and other illustrations

## How to run in your broswer or download and run locally

The simplest way to explore the text, code and data is to click on [binder](https://mybinder.org/v2/gh/bocinsky/robinson2020/master?urlpath=rstudio) to open an instance of RStudio in your browser, which will have the compendium files ready to work with. Binder uses [rocker-project.org Docker] images to ensure a consistent and reproducible computational environment. These Docker images can also be used locally.

You can download the compendium as a zip from from this URL: [master.zip](/archive/master.zip). After unzipping, open the `Proj` file in RStudio, and run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the [DESCRIPTION](/DESCRIPTION) file). Then open `paper.Rmd` and knit to produce the `paper.docx`.

@@

### Acknowledgements

This compendium was created using the `rrtools` package by Ben Marwick: []()
